Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-22 WSSSPE3/report/WSSSPE3_review.tex
Section 3: Keynote: Back to the topic.

>>>>

Returning to the topic of his talk, Turk invited the audience to picture
scientific software as a flower on a landscape under the Sun, which may
represent in this analogy a number of measurable factors such as number of
citations; growth of a community and number of contributors; amount of funding;
prestigious prizes awarded; stability of the community in terms of leadership
transitions, serving community needs, not breaking test suites, and performance
on new architectures. But all these metrics are strictly speaking
\emph{proxies} for the values and the impact scientific software bears. What we
can measure does not give us direct insight---it just gives us proxies of
insight.
